### 2015-12-21 extended-abstract.tex
write second paragraph, move some of outline around

\begin{document}
\begin{center}
  Temporary Trade Barriers: How Long Do They Last?
\end{center}

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions. This project asks a related but distinct question: given that a product receives protection, what detrmines the length of that protection?

\vskip.3in
Need to motivate question
\begin{itemize}
	\item How long do deviations from trade agreement tariffs last? What are the determinants of these deviations?
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
	\item Whether it's a dispute or it's a measure (what does Chad call these?) like AD or escape clause that has not been disputed, it won't be granted for no reason
\end{itemize}

>>>>

\begin{document}
\begin{center}
  Temporary Trade Barriers: How Long Do They Last?\\
	Kristy Buzard
\end{center}

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions. This project asks a related but distinct question: given that a product receives protection, what determines the length of that protection? \\

This question can be addressed in the context of renewals of trade remedies under the WTO agreements. Normally, temporary measures such as anti-dumping and counter-vailing duties have a five-year sunset provision that is subject to renewal by the U.S. International Trade Commission. Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force.

The continued imposition of a TTB is not in general costless. We might assume then, that the International Trade Commission (ITC) only grants renewals when it finds the benefits outweigh the costs.

\vskip.3in
\begin{itemize}
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
\end{itemize}
